\documentclass{article}
\usepackage{../refalg}

\begin{document}
\Makepagesectionhead{MATH 437}{Manifolds}{ARessegetes Stery}

\tableofcontents
\newpage

\def\open{\mathcal{O}}

\section{Preliminary Results from Calculus}

This section is dedicated to proving the following two theorems, which has various implications in differential geometry:

\begin{theorem}[Inverse Function Theorem]\label{thm:inverse function theorem}
    Let $X$, $Y$ be finite-dimensional normed vector space, $\Omega \subseteq X$ an open set, and $f: \Omega \to Y$ a continuously differentiable function. Let $x_0 \in \Omega$. If $\restr{Df}{x_0}$ is invertible, then $f$ is locally $C^{1}$-invertible at $x_0$ (i.e. $f^{-1}$ is $C^1$-continuous), whose derivative satisfies
    \[
        \restr{Df^{-1}}{f(x)} = (\restr{Df}{x})^{-1}
    \]
\end{theorem}
\vspace{1em}

\begin{theorem}[Implicit Function Theorem]\label{thm:implicit function theorem}
    Let $\Omega \subseteq \R^n \times R^m$ be open, with $F \in C^1{\Omega, \R^m}$ s.t. $F(x_0, y_0) = 0$ for $(x_0, y_0) \in \Omega$. If
    \[
        \det \restr{DF(x_0, -)}{y_0} \neq 0
    \]
    then there exists $\varepsilon \in \R$, and $g \in C^1(B_{\varepsilon}(x_0), \R^m)$ s.t.
    \[
        F(x, g(x)) = 0 \qquad \qquad \forall \ x \in B_{\varepsilon}(x_0)
    \]
\end{theorem}

The general setup is to first prove the inverse function theorem, and use it to vastly simplify the proof for the implicit function theorem. An alternative approach is to first prove the implicit function theorem, and then express the derivative of the inverse function in an implicit manner. 

First setup some lemmas for further use in the proof:

\begin{lemma}[Contraction Mapping Principle]\label{lem: contraction mapping principle}
    Let $X$ be a complete normed vector space, and $M$ be a closed subset of $X$. If $f: M \to M$ is Lipschitz continuous with Lipschitz constant less than 1 (a contraction), then there exists a unique $x_0 \in M$ s.t. $f(x_0) = x_0$.
\end{lemma}

\begin{proof}
    Since $X$ is complete and $M$ is closed, it suffices to prove that the sequence given by $(a_n) := f^n(x)$ is Cauchy. The limit must lie in $M$ as otherwise $M$ is not equal to its closure. By hypothesis there exists $C \in [0, 1)$ s.t.
    \[
        \abs{f^2(x) - f(x)} < C \cdot \abs{f(x) - x} \qquad \qquad \forall \ x \in M
    \]
    This gives the approximation
    \[
        \abs{f^m(x) - x} < \sum_{k=0}^{m-1} C^k \abs{f(x) - x} < \left( \sum_{k=0}^{\infty} C^k \right) \cdot \abs{f(x) - x} = \frac{1}{1 - C} \cdot \abs{f(x) - x}
    \]
    which implies that $f^m(x)$ is bounded for all $m$. Further for $m < n$ we have
    \[
        \abs{f^n(x) - f^m(x)} \leq \sum_{k=m}^{n-1} \abs{f^{k+1}(x) - f^k(x)} < \sum_{k=m}^{n-1} C^k \abs{f(x) - x} < C^m \left(\sum_{k=0}^{\infty} C^k \abs{f(x) - x}\right) = \frac{C^m}{1 - C}\abs{f(x) - x}
    \]
    which can be arbitrarily small via specifying $m$ to be arbitrarily large. Therefore $(a_n)$ admits a limit $a$. Then 
    \[
        a = \lim_{n \to \infty} a_n = \lim_{n \to \infty} f(a_n) = f(\lim_{n \to \infty} a_n) = f(a)
    \]
    since $f$ is continuous (as it is Lipschitz continuous), it commutes with taking the limit.

    Uniqueness follows from the fact that if there exists $x_0 \neq x_1$ s.t. $f(x_0) = x_0, f(x_1) = x_1$, then $\abs{x_0 - x_1} = \abs{f(x_0) - f(x_1)}$ which contradicts with the hypothesis.
\end{proof}

\begin{lemma}\label{lem: map norm invertible}
    Let $X$ be a normed vector space, with $L \in \{L \in \GL(X) \mid \norm{L} < 1\}$ then $(\Id - L) \in \GL(X)$. 
\end{lemma}

\begin{proof}
    Consider the series $S = \sum_{i=k}^{\infty} L^k$. This converges as
    \[
        \norm{S} \leq \sum_{i=k}^{\infty} \norm{L}^k = \frac{1}{1 - \norm{L}}
    \]
    which is finite and well-defined as $\norm{L} \in [0, 1)$. Then consider
    \[
        \lim_{n \to \infty}(\Id - L)\cdot S = \Id - \lim_{n \to \infty} L^n = \Id
    \]
    as $\norm{L} < 1$. 
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:inverse function theorem}]
    Without loss of generality, assume $\restr{Df}{x_0} = \Id$; and $x_0 = 0, f(x_0) = 0$. These are done via applying an affine transformation, which preserves the property of being $C^1$-invertible. 

    Consider the approximation of $f$ near $x_0 = 0$: let $g(x) = f(x) - x$. Since $g(0) = 0$ and both $f$ and $\Id$ are continuous, there exists $r$ s.t. $\closure{B_r(x)} \subseteq \Omega$, and $\norm{\restr{Dg}{x}} \leq \frac{1}{2}$ for all $x \in \Omega$. This implies that $g$ is a contraction in $\closure{B_r(0)}$, as
    \[
        g(x) - g(0) = \int_{0}^{x} \restr{Dg}{t} \dt = \int_{0}^{1} \restr{Dg}{xt} x \dt = x\cdot \int_{0}^{1} \restr{Dg}{xt} \dt \implies 
        \norm{g(x)} \leq \sup_{t \in [0, 1]} \norm{\restr{Dg}{xt}} \cdot \norm{x} = \frac{1}{2} \norm{x}
    \]
    This implies that $f$ maps surjectively onto $\closure{B_{r/2}(0)}$: consider $h := y + g(x)$, which is a map from $\closure{B_r(0)}$ to itself. $h$ is also a contraction as
    \[
        \norm{h(x_1) - h(x_2)} = \norm{g(x_1) - g(x_2)} \leq \frac{1}{2} \norm{x_1 - x_2}
    \] 
    Further the space on which $h$ acts is closed.\footnote{The point of taking the closure of $B_r(0)$ in the construction is to apply the contraction mapping principle here, as it requires the space to be closed.} This implies that there exists a fixed point $x_0$ for $h$; but this implies a preimage:
    \[
        x_0 = y + x_0 - f(x_0) \implies f(x_0) = y
    \]
    Then $f$ is a bijection on $\Omega_1 \to f(\Omega_1)$, where $\Omega_1 = f^{-1} B_{r/2}(0) \cap B_r(0)$. The continuity of $f$, and the fact that $g$ is a contraction is preserved through restriction of domain. Therefore we have
    \begin{align*}
        \norm{x_1 - x_2} 
        & = \norm{(f(x_1) - f(x_2)) - (g(x_1) - g(x_2))} \\
        & \leq \norm{f(x_1) - f(x_2)} + \norm{g(x_1) - g(x_2)} \\
        & \leq \norm{f(x_1) - f(x_2)} + \frac{1}{2} \norm{x_1 - x_2}
    \end{align*}
    which implies that 
    \begin{equation}\tag{$\ast$}\label{eq: linear bound on f}
        \frac{1}{2} \norm{x_1 - x_2} \leq \norm{f(x_1) - f(x_2)} \implies \norm{x_1 - x_2} = \norm{f^{-1}(y_1) - f^{-1}(y_2)} \leq 2\norm{y_1 - y_2}
    \end{equation}
    i.e. $y$ is continuous. It is safe to take the inverse as $f$ is a bijection in the domain specified. 

    Now prove the theorem. By the setup we have $\norm{\Id - \restr{Df}{x_1}} = \norm{\restr{Dg}{x_1}} \leq \frac{1}{2}$ for all $x_1 \in \Omega$, which by Lemma \ref{lem: map norm invertible} implies that $\restr{Df}{x}$ is invertible for all such $x$. Since $f$ is differentiable, there exists $\restr{Df}{x_1}$ s.t. 
    \[
        f(x) - f(x_1) = \restr{Df}{x_1} (x - x_1) + o(\norm{x - x_1})
    \]
    for $x \in B_{\eta}(x_1)$ for some $\eta$. This implies that
    \[
        (\restr{Df}{x_1})^{-1}(f(x) - f(x_1)) = (x - x_1) + o(\norm{x - x_1})
    \]
    Further restrict $x_1 \in \Omega_1$ where we have the linear bound \eqref{eq: linear bound on f}. After substituting the variables we have
    \[
        (\restr{Df}{f^{-1}(y_1)})^{-1}(y - y_1) = (f^{-1}(y) - f^{-1}(y_1)) + o(\norm{y - y_1})
    \]
    which gives by the definition of derivative
    \[
        (\restr{Df}{x})^{-1} = \restr{Df^{-1}}{f(x)} 
    \]
    Now consider the chain of functions
    \[
        y \tooh{f^{-1}} f^{-1}y \tooh{Df} \restr{Df}{f^{-1}y} \tooh{(-)^{-1}} (\restr{Df}{f^{-1}y})^{-1}
    \]
    where $Df$ is by hypothesis continuous; and $f^{-1}$ is continuous according to the proof above. This implies that the composition, which is the derivative of the inverse function, is continuous, i.e. $f$ is $C^1$-invertible.
\end{proof}

This greatly simplifies the proof of the Implicit Function Theorem:
\begin{proof}[Proof of Theorem \ref{thm:implicit function theorem}]
    Consider the map $\Phi: \R^n \times \R^m \to \R^n \times \R^m$, $(x, y) \mapsto (x, F(x, y))$. Since $\det DF = \det D\Phi \neq 0$ by Laplace expansion, which implies that $D\Phi$ is invertible. This allows application of Inverse Function Theorem, which implies that there exists $\Psi = \Phi^{-1}$ taking the form of $(x, y) \mapsto (x, G(x, y))$. Now consider specifically
    \[
        (x, 0) = \Phi \circ \Psi(x, 0) = \Phi(x, G(x, 0)) = (x, F(x, G(x, 0)))
    \]
    which implies that there exists $g := G(-, 0)$ satisfying the requirement. Since the inverse function is uniquely determined, such $g$ is also uniquely defined.
\end{proof}

\section{Preliminary Topology}

\begin{definition}[Topological Space]
    A \textbf{topological space} is a pair (X, $\open$), where $X$ is an arbitrary set, and $\open$ a class of subsets of $X$, which satisfies the follows:
    \begin{itemize}
        \item $\emptyset \in \open$, and $X \in \open$.
        \item Let $(\Omega_i)_{i \in I}$ be a (possibly infinite) class of subsets of $X$, then $\bigcup_{i \in I} \Omega_i \in \open$.
        \item Let $(\omega_i)_{i \in I}$ be a finite class of subsets of $X$, then $\bigcap_{i \in I} \omega_i \in \open$.
    \end{itemize}
    Elements of $\open$ are called the \textbf{open sets}. $\open$ (as a class) gives the topology of $X$. 
\end{definition}

\begin{remark}
    If the topology of $X$ is clear, one often denotes the space by simply $X$. 
\end{remark}

\begin{definition}[Hausdorff Space]
    A topological space $(X, \open)$ is a \textbf{Hausdorff space} if for all $x, y \in X$ there exists $\Omega_x, \Omega_y \in \open$ s.t. $x \in \Omega_x, y \in \Omega_y$; and $\Omega_x \cap \Omega_y = \emptyset$.
\end{definition}

\begin{example}
    Choice of topology is very important. Consider the following examples:
    \begin{itemize}
        \item Consider $(\R, \open)$ where $\Omega \in \open$ if and only if for all $x \in \Omega$, there exists $\varepsilon \in \R$ s.t. $(x - \varepsilon, x + \varepsilon) \subseteq \Omega$. This space is Hausdorff as one could choose $\varepsilon_x = \varepsilon_y = \abs{x - y}/4$. This also illustrates why the intersection must be finite, as otherwise one could construct a converging sequence of $\varepsilon$, whose corresponding class of subsets intersecting to a closed interval.
        \item Consider $(\R, \open)$ to be the trivial topology, where $\open := \{\R, \emptyset\}$. Then the only subset in $\open$ containing $x$ and $y$ is $\R$, which implies that the space is not Hausdorff.
    \end{itemize}
\end{example}

\begin{definition}[Basis of a Topology]
    Let $(X, \open)$ be a topology space. Then a subset $\mathcal{B} \subseteq \open$ is a \textbf{basis of topology} $\open$ if for any $\Omega \in \open$ it can be expressed as union of elements in $\mathcal{B}$. If there exists such $\mathcal{B}$ s.t. it is countably infinite, then $X$ admits a \textbf{countable basis of topology}.
\end{definition}

\begin{proposition}
    $(\R, \open)$ with topology defined as in the first case in the example above admits a countable basis of topology.
\end{proposition}

\begin{proof}
    First consider $\mathcal{B} := \{(a, b) \mid a < b, a, b \in \R\}$. This gives a basis for the topology of $(\R, \open)$ in the sense of the first case above:
    \begin{itemize}
        \item \emph{Any union of elements in $\mathcal{B}$ is open.} Denote such union to be $\Omega$. By construction, for $x \in \R$ s.t. $x \in \Omega$, there exists $a_x < b_x$ s.t. $x \in (a_x, b_x)$. Then there exists $\varepsilon = \min\{x - a_x, b_x - x\} / 2$ that satisfies the definition.
        \item \emph{Any open subset of $\R$ can be expressed as a union of open intervals}. Recall that the union can be infinite. Now consider for $\Omega$ an open interval
        \[
            \Omega = \bigcup_{x \in \Omega} (x - \varepsilon_x, x + \varepsilon_x)
        \]
        where for each $x$, $\varepsilon_x$ is the corresponding radius s.t. the definition is satisfied; and for all $x \in \Omega$, $(\R \smallsetminus \Omega) \cap (x - 2\varepsilon_x, x + 2\varepsilon_x) \neq \emptyset$. By definition for all $x \in \Omega$ there exists such an interval that $x$ is in it.
    \end{itemize}
    Then consider $\mathcal{B}' := \{(a, b) \mid a < b, a, b \in \Q\}$. Since $\Q$ is dense in $\R$, for any $x' \in \R \cap \Omega$ there exists a sequence $(x_n)$ s.t. $\lim_{n \to \infty} x_n = x'$. Choose the sequence s.t. $\abs{x_n - x'} > 2\abs{x_{n+1} - x'}$. Suppose that for all $n$, $x' \notin (x_n - \varepsilon_{x_n}, x_n + \varepsilon_{x_n})$. Then there exists some $n_0$ s.t. $(x_{n+1} - \varepsilon_{x_{n+1}}, x_{n+1} + \varepsilon_{x_{n+1}}) \subsetneq (x_n, x')$ assuming $x_n < x'$ without loss of generality, which is a contradiction.

    Since $\Q \simeq \N \times \N$ which is countable, $\Q \times \Q$ is also countable, indicating that $\beta'$ gives a countable basis of topology on $\R$.
\end{proof}

\begin{remark}
    For $\R^n$, the \underline{standard topology} is defined as where a set $\Omega$ is open if and only if for every $x \in \Omega$ there exists $\varepsilon > 0$ s.t. $B_{\varepsilon}^n (x) \subseteq \Omega$. 
\end{remark}

\begin{corollary}\label{cor: R^n countable basis}
    By the same proof, and considering open intervals as $1$-balls on $\R^1$, this gives that $\R^n$ with the standard topology admits a countable basis of topology. 
\end{corollary}

\begin{definition}[Induced Topology]
    Let $(X, \open_X)$ be a topological space, and $Y \subseteq X$. Then there exists a definition for $\open_Y$ where $\Omega' \in \open_Y$ if and only if there exists $\Omega \in \open_X$ s.t. $\Omega' = \Omega \cap Y$. This is the \textbf{induced topology} on $Y$.
\end{definition}

\begin{definition}
    Let $(X_1, \open_1)$, $(X_2, \open_2)$ be topological spaces. Then
    \begin{itemize}
        \item A map $f: X_1 \to X_2$ is \textbf{continuous} if for all $\Omega \in \open_2$, $f^{-1}(\Omega) \in \open_1$. 
        \item A map $f: X_1 \to X_2$ is \textbf{homeomorphic} if it is invertible, and both $f$ and $f^{-1}$ are continuous. 
    \end{itemize}
\end{definition}

\begin{example}
    The map $f: [0, 2\pi) \to S^1, x \mapsto (\cos x, \sin x)$ is not homeomorphic, as for the arcs wrapped around the origin (e.g. $f([0, \pi/6) \cup (11\pi/6, 2\pi))$) the image is open, but the interval itself is not open.
\end{example}

\begin{definition}[Diffeomorphism]
    Let $\Omega_1, \Omega_2 \subseteq \R^n$ be open sets. Then a homeomorphism $f: \Omega_1 \to \Omega_2$ is a \textbf{diffeomorphism} if both $f$ and $f^{-1}$ are differentiable. Similarly one can consider $C^k$-diffeomorphism for $f$ and $f^{-1}$ being $k$-times differentiable.
\end{definition}

\begin{proposition}
    If $f$ is a diffeomorphism which is $n$-times differentiable, then $f^{-1}$ is also $n$-times differentiable.
\end{proposition}

\begin{proof}
    Proceed to prove this via induction on $k$:
    \begin{itemize}
        \item \emph{Base case}. For $k = 1$, this is by the definition of diffeomorphisms.
        \item \emph{Inductive step}. Suppose that this is proven for $k = m$. For $k = m+1 \leq n$, since $f$ is $C^n$-differentiable and locally injective everywhere, by inverse function theorem this gives
        \[
            g'(x) = (f'(g(x)))^{-1}
        \]
        where by hypothesis $f'$ and $g$ are both $C^m$-differentiable, and therefore so is their composition and $g'$.
    \end{itemize}
    This gives $g'$ is $C^{n-1}$-differentiable, which gives $g$ being $C^n$-differentiable.
\end{proof}

\begin{remark}
    A differentiable homeomorphism is not necessarily a diffeomorphism, as $f$ is not necessarily locally injective everywhere. Consider $f: x \mapsto x^3$ whose inverse is not differentiable at $0$. $f$ is not locally injective at 0.  
\end{remark}

\section{Differentiable Manifolds}

\begin{definition}[Manifold]
    An \textbf{$n$-dimensional topological manifold ($n$-manifold)} $M$ is a Hausdorff space with a countable basis of topology s.t. for every $p \in M$ there exists an open $U(p)$ s.t. there exists a homeomorphism $\varphi_p: U(p) \to \Omega \subseteq R^n$.
\end{definition}

\begin{definition}[Chart; Atlas; Compatibility]
    For the homeomorphisms defined as above, the pair $(U(p), \varphi_p)$ is an \textbf{$n$-dimensional chart}. An \textbf{atlas} is a set of charts whose domains $U(p)$ covers the whole space $M$, i.e. for all $r \in M$, there exists $p \in M$ s.t. the corresponding chart $(U(p), \varphi_p)$ satisfies $r \in U(p)$. 

    Given two $n$-charts $(U, \varphi)$ and $(V, \psi)$, a \textbf{change of chart} between the charts is a map
    \[
        \psi \circ \varphi^{-1} : \varphi(U \cap V) \to \psi(U \cap V) \in \{f \mid f: \R^n \to \R^n\}
    \]
    These two charts are \textbf{compatible} if the change of chart is a $C^{\infty}$-diffeomorphism. An atlas where all charts are compatible is a $C^{\infty}$-atlas.
\end{definition}

\begin{definition}[Smooth Manifold]
    An $n$-manifold is \textbf{smooth (differentiable)} if it admits a maximal $C^{\infty}$-atlas (as a set). 
\end{definition}

\begin{remark}
    Since the atlas is required to be $C^{\infty}$, it suffices to consider the equivalence class via specifying an atlas whose domains cover the whole manifold, and consider the atlas thus spanned. There exists manifolds that are not smooth (i.e. does not admit a $C^{\infty}$-atlas) if for all valid charts the maximal set of charts spanned by it does not cover the whole manifold.
    
    Under the context of smooth manifolds, one will not consider atlases that are not $C^{\infty}$, but instead consider this manifold as not having an atlas.
\end{remark}

The followings studies a particular example of manifolds:

\begin{definition}[Projective Space]
    Consider the equivalence relation for $x, y \in \R^{n+1}$ where $x \sim y$ if and only if there exists $\lambda \in \R$ s.t. $\lambda x = y$. The \textbf{$n$-dimensional real projective space} is defined as $\R^{n+1}/(\sim) =: P(\R^{n+1})$, which is often denoted as $\RP^n$.
\end{definition}

\begin{proposition}
    $\RP^n$ is a smooth $n$-manifold.
\end{proposition}

\begin{proof}
    To specify the manifold structure it suffices to give the topology together with an atlas. 

    First consider the \underline{quotient topology} of the projective space: let $\pi: \R^{n+1} \smallsetminus \{0\} \to \RP^n$ be the quotient map specified by the equivalence class each point represents. Define $\Omega' \subseteq \RP^n$ to be open if and only if $f^{-1}(\Omega')$ is open. The topology is indeed well-defined as $\pi$ commutes with both intersection and union of sets. This also implies that $\RP^n$ admits a countable basis of topology, as by Corollary \ref{cor: R^n countable basis} $\R^{n}$ is compact for all finite $n$.

    Further consider the charts given by
    \[
        \varphi_i: \RP^n \to \R^n, \qquad \overline{(x_1, \cdots, x_{n+1})} \mapsto \frac{1}{x_{i}} (x_1, \cdots, x_{i-1}, x_{i+1}, \cdots, x_{n})
    \]
    where $\varphi_i$ is defined for all $x \in X_i := \{x \in \RP^n \mid \forall\  \overline{(x_1, \cdots, x_{n+1})} \in [x], x_i \neq 0\}$. This is clearly open as for all $\tilde{x} \in X_i$, $B_{\tilde{x}_i/2}(\tilde{x}) \subseteq X_i$. Domains of $\varphi_i$s cover the whole space, as for any $y \in \RP^n$, every representative $\tilde{y}$ of $y$ must have at least some field $\tilde{y}_j$ that is nonzero. Then it is covered by the domain of $\varphi_j$. Change of charts is linear according to the construction above, and therefore is smooth.
\end{proof}

\begin{remark}
    $\RP^n$ is further compact, as it can be considered as $S^n / (\sim)$ where points sharing the same diameter are considered to be equivalent. The quotient topology implies that $\pi: \RP^n \to S^n / (\sim)$ is continuous. Therefore, $\RP^n$ is compact as $S^n$ is. 
    
    Notice that continuous maps preserve compactness. Let $f: M \to N$ be continuous. Then every open cover of $N$ corresponds to an open cover of $M$, which by compactness of $M$ gives a finite sub-cover $U$. Then $f(U)$ gives a finite open cover of $N$. 
\end{remark}

\begin{definition}[Submanifold]
    Let $N$ be a smooth $n$-manifold, and $\mathcal{A}$ be its atlas (which is $C^{\infty}$). Then an \textbf{$m$-dimensional submanifold} $M$ of $N$ is a subset $M$ of $N$ s.t. for all $p$ there exists a chart $(U, \varphi_p)$ which is in some maximal atlas of $N$ s.t.
    \[
        M \cap U(p) = \varphi^{-1}(\varphi(U) \cap (\R^m \times \{0\}))
    \] 
    Then $(U \cap M, \restr{\varphi_p}{M})$ is called the \textbf{adapted chart}; and $(n - m)$ is the \textbf{codimension} of $M$ in $N$.
\end{definition}

\begin{remark}
    Every submanifold is in itself a manifold, as restriction of topology preserves Hausdorff property and a countable basis of topology.
\end{remark}]

\begin{definition}[Smooth Maps]
    Consider smooth maps in general between smooth manifolds:
    \begin{itemize}
        \item Let $(M, \mathcal{A})$ and $(N, \mathcal{A}')$ be two smooth manifolds. Then $F: M \to N$ is \textbf{smooth} if for $(U, \varphi_p) \in \mathcal{A}$ and $(V, \varphi_{F(p)}') \in \mathcal{A}'$ the map
        \[
            \varphi_{F(p)}' \circ F \circ \varphi_P^{-1} : \varphi_P(U \cap F^{-1}(V)) \to \varphi_{F(p)}' (F(U) \cap V)
        \]
        is smooth as an endomorphism on $\R^n$.
        \item Let $I \subseteq \R$ be an interval. Then a \textbf{smooth curve} on $M$ is a curve with a parameterization $\gamma: I \to M$ that is smooth (considered as a map between manifolds). 
        \item $f: M \to \R$ is a \textbf{smooth function} if $f$ is smooth as a map between manifolds. Smooth functions on $M$ are denoted by $C^{\infty}(M)$.
    \end{itemize}
\end{definition}

\begin{definition}
    If $F: M \to N$ is smooth, with $F^{-1}$ exists and is smooth, then $F$ is a \textbf{diffeomorphism}, with $M$ and $N$ \textbf{diffeomorphic}. Diffeomorphisms that are endomorphisms on $M$ are denoted as $\Diff(M)$, or $\Diffeo(M)$.
\end{definition}

In the next section, more details of smooth manifolds will be discussed, which will lead to natural (and general) construction of submanifolds.

\section{Tangent Space and the Differential}

\end{document}
